%% start of file `resume.tex'.

% possible options include font size ('10pt', '11pt' and '12pt'),
% paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper',
%'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\documentclass[11pt,letter,roman]{moderncv}
% set input encoding
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% URW Garamond
%\renewcommand{\rmdefault}{ugm}
% URW Classico (Optima)
%\renewcommand{\sfdefault}{uop}
% Enable bold garamond, smallcaps
\usepackage{garamondx}
% add multi-column support
\usepackage{multicol}

% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{banking}
% color options 'blue' (default), 'orange', 'green', 'red',
% 'purple', 'grey' and 'black'
\moderncvcolor{black}
% to set the default font; use '\sfdefault' for the default sans serif font,
% '\rmdefault' for the default roman one, or any tex font name
\renewcommand{\familydefault}{\rmdefault}
% uncomment to suppress automatic page numbering for CVs longer than one page
\nopagenumbers{}

% adjust the page margins
\usepackage[scale=0.815]{geometry}
% if you want to change the width of the column with the dates
\setlength{\hintscolumnwidth}{3cm}

% insert personally identifiable information (name, address, etc.)
\input{pii.tex}

%-----        content     ----------------------------------------------------
\begin{document}
%-----       resume       ----------------------------------------------------
\makecvtitle{}
\vspace{-\baselineskip}

\section{\textsc{Summary of Qualifications}}
A Senior DevOps Engineer with proven skills in creating, automating and
managing highly complex, business critical services on-premise and in the
cloud, with a demonstrated tenacity for innovation, collaboration and
improvement. Works best when challenged with new technologies and problems and
given creative freedom to come up with solutions. Always learning and applying
new concepts and skills and enjoys contributing to open source software.

\section{\textsc{Technical Skills}}
\cvitem{Languages (Proficient)}{Go, C\#, PowerShell, Python, SQL}
\cvitem{Languages (Basic)}{Ruby, Bash scripting, Javascript, C, Lua, Erlang, LaTeX}
\cvitem{Cloud Services}{Amazon Web Services, Windows Azure, SoftLayer}
\cvitem{Automation}{SaltStack, Chef, Docker, Orchestrator 2012}
\cvitem{Infrastructure Tools}{Logstash, Consul, Microsoft System Center Operations Manager}
\cvitem{Data Services}{ElasticSearch, InfluxDB, PostgreSQL, Microsoft SQL Server}

\section{\textsc{Work Experience}}
\cventry{06/2014 -- 09/2015}{Senior DevOps Engineer}{PlayFab, Inc.}
{Seattle, WA}{}{%
  \begin{itemize}
    \item As one of the first-round engineering hires at PlayFab, designed and
      built a scalable server management stack for all of PlayFab's services.
      This allowed PlayFab engineers to build, test, and deploy new versions of
      the company's core services in under 15 minutes as well as saving the
      company \$500,000 in AWS costs over a 12 month period.
      \begin{itemize}
        \item Built continuous integration and test automation on Jenkins to
          automate deployments to Amazon Elastic Beanstalk.
        \item Deployed Consul clusters in multiple datacenters to provide
          service discovery and monitoring.
        \item Developed scripted deployment of Windows and Linux servers using
          masterless SaltStack with state storage in S3.
        \item Developed a data pipeline using Heka as an event stream router
          and performance data collector, with ElasticSearch and InfluxDB as
          backends for log and performance metrics.
        \item Saved time for developers every day by building internal
          dashboards using Kibana, Grafana and the Consul web UI to expose log,
          performance and health data.
      \end{itemize}
    \item Ported the Consul API from Go to C\# and open-sourced the library as
      \textbf{Consul.NET}. This library is used by PlayFab services written in
      C\# to take advantage of the distributed lock and highly consistent
      key/value pair storage provided by Consul as well as monitor multi-region
      health checks for an Azure-based status page.
    \item Redesigned and upgraded PlayFab's \textbf{ejabberd} infrastructure,
      which was used to provide game chat services. Wrote an ejabberdctl
      cluster join/leave module in Erlang to use as part of an AWS autoscaling
      process.
  \end{itemize}
}

\cventry{12/2013 -- 06/2014}{Windows Server Engineer}{Nordstrom}
{Seattle, WA}{ITS Department}{%
  \begin{itemize}
    \item Developed build and configuration management automation for Windows
      servers using Ruby and Chef.
    \item Developed resource providers using Ruby FFI to allow Chef to
      configure services via native Windows APIs.
    \item Managed monthly patching and updates for over 4000 Windows servers
      using WSUS.
  \end{itemize}
}
\cventry{05/2013 -- 11/2013}{Systems Engineer}
{Microsoft (via Wimmer Solutions)}{Redmond, WA}{Office 365 Dedicated}{%
  \begin{itemize}
    \item Developed a series of SCOM management packs to create a development
      pattern based on PowerShell and Orchestrator to support automatic
      resolution of 36\% of monitoring-generated incidents.
    \item Developed Windows services in C\# to integrate a custom ticketing
      system, CMDB and SCOM.
    \item Maintained System Center Orchestrator and System Center Operations
      Manager infrastructure to support automation and monitoring for over
      5000 servers.
  \end{itemize}
}
\cventry{07/2011 -- 05/2013}{Senior Systems Engineer}
{Avanade, Inc.}{Seattle, WA}{ITS Department}{%
  \begin{itemize}
    \item Trained and managed a six member global Tier II team spanning the
      U.S.A., India, Argentina, and the Philippines to provide technical,
      product, and development support for SharePoint platforms.
    \item Improved project development teams' deployment practices and
      operational sustainability by giving feedback with examples, which
      reduced time taken to execute changes by an average of 60\%.
    \item Designed and implemented a knowledge management system using C\#,
      JavaScript and XML to document systems operation and troubleshooting
      procedures; integrated SCSM knowledge article features with SharePoint
      Server as a CMS and SharePoint Business Data Services as a data bus.
    \item Developed a suite of PowerShell scripts automate common tasks
      relating to managing a SharePoint farm, reducing user error and reducing
      the response time for common service requests.
    \item Maintained 99.9\% uptime on five business-critical SharePoint
      Server farms using SharePoint and SQL high availability technologies and
      Akamai traffic management services.
    \item Designed and implemented SCOM management packs to provide
      monitoring, performance alerts, and reporting for nine internal line of
      business applications; reduced alert response time to
      under thirty minutes.
  \end{itemize}
}
\cventry{04/2010 -- 07/2011}{Infrastructure Analyst}
{Avanade, Inc.}{Seattle, WA}{Consulting}{%
  \textbf{Microsoft -- MSCIS -- SCOM Application Mapping}
  \begin{itemize}
    \item Managed a globally distributed five-member development team to
      gather information about, model and monitor 39 complex multi-tier
      applications.
    \item Supervised the creation of SCOM distributed application management
      packs for each application, while meeting an aggressive
      one-month delivery deadline.
  \end{itemize}
  \textbf{Microsoft -- Xbox Live Operations -- Monitoring Maturity Improvement}
  \begin{itemize}
    \item Supervised an eight-member offshore development team creating
      process documentation and management packs for critical Xbox Live
      services, including the Zune Marketplace, Xbox Marketplace, and Xbox
      game matchmaking services.
    \item Reduced SCOM alert volume and noise for the entire Xbox Live
      operations center from 200K duplicated alerts to forty relevant alerts
      per month.
    \item Developed SCSM workflow code to automatically link incidents created
      in Service Manager by Operations Manager alerts to knowledge articles
      stored in Service Manager.
  \end{itemize}
  \textbf{Wireless Telecommunications Provider -- Internal IT}
  \begin{itemize}
    \item Increased accountability and simplified IT operation practices by
      developing custom SharePoint workflows and training two team members
      on SharePoint technology support.
    \item Maintained production Active Directory and Microsoft Office
      SharePoint Server 2007 environments.
  \end{itemize}
}

\section{\textsc{Additional Work Experience}}
\cventry{01/2010 -- 04/2010}{Systems Engineer}
{Microsoft (via TEKSystems)}{Redmond, WA}{BPOS-S}{}
\cventry{04/2009 -- 12/2009}{Operations Engineer}
{Avanade, Inc. (via Triad Group)}{Seattle, WA}{ITS Department}{}
\cventry{09/2008 -- 04/2009}{Systems Engineer}
{Microsoft (via Compucom)}{Redmond, WA}{Windows Team}{}
\cventry{07/2007 -- 07/2008}{Support Engineer}
{Microsoft (via VMC)}{Fargo, ND}{Premier Support Services}{}

%\section{\textsc{Industry Certifications}}
%\cvitem{MCSE}{SharePoint, Private Cloud}
%\cvitem{MCITP}{Enterprise Administrator on Windows Server 2008,
%SharePoint Administrator 2010}
%\cvitem{MCSA}{Windows Server 2012}

\section{\textsc{Education}}
\label{sec:Education}
\cventry{Graduated 2007}{Associate of Applied Science (A.A.S.)}
{North Dakota State College of Science}{Wahpeton, ND}{GPA: 4.0}
{Major: Computer Information Systems}

\end{document}
%% end of file `resume.tex'.
